{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-05-02 bmvc_review.tex
Paper trimmed for 9 pages Limit - Excluding References

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications for embedded systems. This is primarily because most of
embedded systems already includes image acquisition pipeline and a
tremendous amount of progresses on research has been made for many
areas in computer vision. However, to successfully deploy a computer
vision algorithm on any existing embedded systems, a vision algorithm
needs to satisfy, at least, two criteria: minimal, manual intervention
after deployment and small footprint of computing resource consumption
and on executable code, with the assumption of reasonably good
performance. To this end, in this paper, we propose an ensemble of the
kernelized correlation filters (KCF), we call {\it E}nKCF, for a
single-target object tracking. In particular, we developed a committee
of KCFs to specifically address the scale-change and dynamic maneuver
of the target over frames. In addition, we devised a Bayes filter for
a smooth transition between individual KCFs' executions. Also, we
slightly modify the {\it E}nKCF to perform tracking in low frame rate
videos dominated by large ego-motion.  large ego-motion.  To verify
the usefulness of the proposed method, we compared the performance of
ours to those of the existing online tracking methods. Experimental
results showed that the performance of ours are 72.53\% for precision
on 20 pixels and 52.90\% for success rate for OTB100 data, and 55.71\%
and 41.71\% for UAV123 data. These results confirmed that our method
outperformed the existing ones over 5\% on precision on 20 pixels and
10-20\% on AUC on average. Our implementation ran at 340 fps for
OTB100 and at 416 fps for UAV123 data that is faster than DCF (292
fps) for OTB100 and KCF (292 fps), DCF (457 fps), and STC (350 fps)
for UAV123.
\end{abstract}

@@

The proposed algorithm, {\it E}nKCF, deploys three KCFs in turn: The
first filter, $R_{t}^{S}$, focuses on learning the target area and its
background, \textit{target}+\textit{small background} for addressing a
marginal translation by a target, the second filter, $R_{s}$, focuses
entirely on learning the target's scale, \textit{target-only}, and the
last filter, $R_{t}^{L}$, focuses on the target area and its
background twice bigger than that of the first filter, $R_{t}^{S}$,
\textit{target}+\textit{large background}. We set up {\it E}nKCF in
this way because we believe a correlation filter for learning a
target's translation should include its background to better
discriminate the target from its background and another correlation
filter is prepared to focus on the target itself to estimate the right
size or scale of the target. Fig.~\ref{fig:Filters} shows examples
of the region of interest (ROI) covered by each of three filters. We
believe that a filter for learning a target's translation should
include its background. In addition, making the ROI for the scale
filter, $R_{s}$, tighter reduces the size of the template for the
elementwise multiplication, resulting in a scale estimation in a
higher speed.
\begin{figure}[!h]
\centering
\includegraphics[width=0.5\textwidth]{figures/Filters_Details.pdf}
\caption{The three filters denoted as \textit{target+small background} translation filter,
  \textit{target-only} scale filter and \textit{target+large background} translation filters are
  shown. Also, the hanning window and desired Gaussian response for
  each filter is displayed.}
\label{fig:Filters}
\end{figure}

@@

In summary, the scale filter, $R_{s}$, is designed to directly handle
the scale change of a target and provides $R_{t}^{L}$ and $R_{t}^{S}$
with more focused ROIs about the target's translation. A translation
filter, $R_{t}^{L}$, is intended to look at a larger search area to
estimate the target's translation and recover from any potential
drifts. Another translation filter, $R_{t}^{S}$, on the other hand, is
designed to addresses the drawback of $R_{t}^{L}$ that it may learn
noisy shape features due to its large search area. Figure
\ref{Workflows} illustrates the workflow of the proposed
algorithm and alg.\ref{alg:MKCF} shows the pseudo-code of {\it
  E}nKCF. We do not have a seperate pseudeo-code for {\it E}nKCF2 as there are only two differences between 
  {\it E}nKCF and {\it E}nKCF2. First, the {\it E}nKCF2 runs $R_{t}^{L}$ every frame
to better tackle large ego-motion at low video frame rates. Second, we remove the particle filter in the {\it E}nKCF2 
tracker due to large ego-motion. In the following section, we will briefly mention the theory
behind the KCF.

\begin{algorithm}
	\caption{The {\it E}nKCF Tracking Algorithm.}\label{alg:MKCF}
	\begin{algorithmic}[1]
	\State \textbf{Input} : Initial bounding box $x_{0}$, frame counter $fc$, scale filter frequency $n = 5$,
	\State \textbf{Output} : 
				\If{$fc\:\%\:n=0$} \Comment{Condition 1}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
						Scale filter (\textit{target-only}) model $R_{s}$.
			     \EndIf
				\If{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=2$}\Comment{Condition 2}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t_1})$,
						Large Area Translation Filter model $R_{t}^{L}$.
				\EndIf
				\If{$fc\:\%\:n=3\:\:or\:\:fc\:\%\:n=4$}\Comment{Condition 3}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
						Small Area Translation Filter model $R_{t}^{S}$.
				\EndIf
	\Procedure{track}{$x_{t-1},y_{t-1},s_{t-1}$} 
				\State // Translation Estimation
				\State Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $x_{t} = (x_{t},y_{t},s_{t-1})$;
				\State // Translation Estimation
				\State Crop the ROI for the $R_{t}^{L}$, or $R_{t}^{S}$ given $x_{t}$
				and estimate translation ($x_{t}$,$y_{t}$) using $R_{t}^{L}$ (Condition 2) or $R_{t}^{S}$ (Condition 3),
				\State Skip translation estimation for $R_{s}$ (Condition 1);
				\State // Scale Estimation
			    \State Crop the ROI for the $R_{s}$ and estimate scale, $s_{t}$, using $R_{s}$ (Condition 1), 
				\State Scale pool for $R_{s}$ : $\lbrace1.05,1.0,1/1.05\rbrace$;
		        \State Skip it for $R_{t}^{L}$ and $R_{t}^{S}$ (Condition 1, and 2),
				\State // Update Translation
				\State Perform Importance Re-sampling (if necessary) for Particle Filter and compute the mean of posterior pdf $x_{t} = (x_{t},y_{t},s_{t})$;
			    \State // Model Update
				\If{$PSR(y_{R_{s}}) \geq T_{R_{s}}$}
				\State Update $R_{s}$ (Condition 1);
				\EndIf							 
				\If{$PSR(y_{R_{t}^{L}}) \geq T_{R_{t}^{L}}$} 
				\State Update $R_{t}^{L}$ (Condition 2);
				\EndIf	
			     \If{$PSR(y_{R_{t}^{S}}) \geq T_{R_{t}^{S}}$}
				\State Update $R_{t}^{S}$ (Condition 3);
			     \EndIf		
	\EndProcedure	
	\end{algorithmic}
\end{algorithm}

\begin{comment}
{\it Burak: The KCF section doesn't fit the section before and
  after. In addition, it's still too long.}

@@

\subsection{Kernelized Correlation Filter} \label{sec:kcf}
The Kernelized Correlation Filter tracker has recently been
increasingly popular due to its operation at hundreds of frames per
second with state-of-the-art tracking capabilities even in challenging
cases. Its computational efficiency arises from its use of the
discrete fourier transform of the circulant matrix and frequency
domain element-wise operations known as hadamard product and
division. The first example of frequency domain trackers is the MOSSE
tracker running at $700$fps \cite{bolme2010visual}. It minimizes the
ridge regression function in the frequency domain using a single
template and intensity features. The KCF tracker, on the other hand,
minimizes the regularized ridge regression function shown below.
\begin{equation}
E(h) = \frac{1}{2}||y-\sum_{c=1}^{C}h_{c}*x_{c}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||h_{c}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where $y$ represents the desired continous response whereas $h$ and
$x_{c}$ represents the learned correlation filter and training
template for the given channel. The $c$ parameter included in
\cite{henriques2015high,galoogahi2013multi} makes it possible to
integrate multi-channel features such as HoG and colour into the ridge
regression function. The closed-form solution for the
eq.~\ref{eq:Closedform_RidgeReg} can be obtained by setting the
derivative of $E$ w.r.t $w$ to $0$. The primal solution in the
frequency domain is formulated as
%\begin{equation}
%w = (X^{T}X+\lambda)^{-1}y
%\label{eq:SpatialSolution}
%\end{equation}
\begin{equation}
w = (X^{H}X+\lambda I)^{-1}X^{T}y
\label{eq:FourierSolution}
\end{equation}
where $X^{H}$ and $\lambda$represent the complex-conjugate of training
samples and regularization term. More documentation on the spatial and
fourier domain solutions can be found in \cite{henriques2015high}. The
MOSSE tracker uses one training sample centred at estimated position
of the target. This framework does not include enough background
information into the learned model,$w$. The application of the
circulant matrix theorem into the eq.~\ref{eq:Closedform_RidgeReg}
makes it possible to include many background patches at a similar
computational complexity. A circulant matrix includes the circularly
shifted patches of the positive training sample $x$ by a cylic shift
operator.

@@

In this form, the equation \ref{eq:FourierSolution} could prohibit us
from implementing a high speed object tracking as we need to perform
large number of element-wise division and multiplication
operations. However, we know from \cite{gray2006toeplitz} that all
circulant matrices are represented diagonally by the Fourier Transform
regardless of the base sample $x$.
%\begin{equation}
%X = Fdiag(\hat{x})F^{H},
%\label{eq:CirculantMatrixDFT}
%\end{equation}
%where $F$ denotes a constant Fourier Transform matrix and $x$ is the
%Discrete Fourier Transform of the base sample $x$. 
%To simplify the
%cost function formulation in eq.~\ref{eq:FourierSolution} we multiply
%$X$ in eq.~\ref{eq:CirculantMatrixDFT} with $X^{H}$ yielding
%\begin{equation}
%X^{H}X = Fdiag(\hat{x}^{*}\odot \hat{x})F^{H}.
%\label{eq:SimplificationX} 
%\end{equation}
Then, the optimized solution vector in the Fourier domain $\hat{w}$ is formulated as
\begin{equation}
\hat{w} = \hat{x}^{*}*\hat{y}(\hat{x}^{*}*\hat{x}+\lambda)^{-1}.
\label{eq:DiagonalizedPrimalSolution}
\end{equation}
To further improve the robustness to geometric and photographic variations, one can exploit non-linear
regression function in the Correlation Filter framework \cite{henriques2015high}. 
%\begin{equation}
%\alpha = y(K+\lambda I)^{-1}
%\end{equation}
%where $K$ and $\alpha$ represent the kernel matrix and corresponding
%dual space solution. 
%\cite{henriques2015high} states that kernel
%matrices is circulant for datasets of circular cylic satisfying the
%following theorem.
%\begin{equation}
%k(x,x^{'}) = k(Mx,Mx^{'}),
%\label{eq:KernelCirculantTheorem}
%\end{equation}
%where $M$ represents the permutation matrix. Some kernels satisfying
%the eq.~\ref{eq:KernelCirculantTheorem} are \textit{Gaussian},
%\textit{Polynomial}, \textit{Intersection} and \textit{Hellinger}
%kernels. 
Similar to the diagonalization in the linear ridge regression
solution in eq.~\ref{eq:DiagonalizedPrimalSolution}, the kernelized
ridge regression can be made diagonal using the same circulant matrix
theorem.  The diagonalized Fourier domain dual form solution can be
expressed as
\begin{equation}
\hat{\alpha} = \hat{y}(\hat{k}^{xx}+\lambda)^{-1}
\label{eq:FourierDualDomainSolution}
\end{equation}
where $\hat{k}^{xx}$ represents the first row of the Kernel matrix $K$
known as \textit{gram matrix}. In this study, we will only focus on
application of the Gaussian Kernel to the Correlation Filters. We
refer the readers to \cite{henriques2015high} for the detailed
documentation of the application of other kernels to the Correlation
Filters. The Gaussian kernelization is
expressed as
\begin{equation}
k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\hat{x}_{c}^{*}\odot \hat{x}_{c}^{'}))).
\label{eq:GaussianCorrelationSingleChannel}
\end{equation}
%\begin{equation}
%k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\hat{x}^{*}\odot \hat{x}^{'})))
%\label{eq:GaussianCorrelationSingleChannel}
%\end{equation}
The first correlation filter based trackers used grayscale feature ($C=1$) to
learn the solution vector $w$, however, multi-channel features
such as HoG and Color were later exploited to improve tracking
accuracy \cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. The
multi-channel feature integration into the Gaussian Kernelization
function in eq.~\ref{eq:GaussianCorrelationSingleChannel} is achieved
in a very straight-forward way by summing the correlation result over the channels.

Training shown in eq.~\ref{eq:FourierDualDomainSolution}
gives us $\hat{a}$ learned in time step $t$. We can accumulate
$\hat{a}$ over time to integrate more temporal information. This can
be expressed as
\begin{equation}
\hat{a}_{t} = (1-\beta)\hat{a}_{t-1} + \beta\hat{a}_{t}. 
\end{equation}

Finally, detection step in multi-channel KCF framework is performed as
\begin{equation}
r(z) = F^{-1}(\hat{k}^{xz} \odot \hat{\alpha})
\end{equation}
where $r$ denotes the correlation response at all cylic shifts of the
first row of the kernel matrix $K$. The peak point of the response
function gives us the estimated translation of the object from time
step $t$-$1$ to $t$.

@@

\textbf{Finding Optimal Hyperparameters} Each of three KCFs in {\it
  E}nKCF is designed for addressing a specific challenge of a single,
target tracking problem. Thus each of them should have different value
for the optimal parameters. For instance, the primary task of the
translation filter, $R_{t}^{L}$ is to estimate the translation of a
target from the previous frame whereas the scale filter, $R_{s}$ and
the estimated state of the particle filter are primarily used to
estimate the scale and translation. Because of this, we set the
learning rates ($\beta$) of individual filters, $R_{t}^{L}$,
$R_{t}^{S}$, and $R_{s}$ differently as $0.020$, $0.020$ and
$0.010$. The desired template response and hanning window for each KCF is shown in fig.~\ref{fig:Filters}.
For the kernel of the Gaussian neighboring function, we empirically
found the optimal values of $\alpha$ as $0.6$, $0.4$, and $0.4$ for
$R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$, and the learning rate as $0.12$
for $R_{t}^{L}$.

We tuned the number of particles in the particle filter to $1000$ after carrying out experiments, 
The re-sampling is only performed when the \textit{efficient number of samples} (eq.~\ref{eq:Neff_PF}) is lower than a
pre-defined threshold. This way, we can continuously keep reasonable variance among particles.
\begin{equation}
	\hat{N}_{eff} \approx \dfrac{1}{\sum_{p=1}^{P}w_{p}^{2}}
	\label{eq:Neff_PF}
\end{equation}

@@

\begin{figure}
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=4.00cm]{./figures/Precision_UAV123.pdf}}
\bmvaHangBox{\includegraphics[width=4.0cm]{./figures/Success_UAV123.pdf}}\\
\end{tabular}
\caption{Evaluation and comparison of the proposed {\it E}nKCF tracker on the UAV123 dataset. UAV123 Dataset consists of $123$ video sequences captured from a micro UAV including large camera motion, low resolution objects, partial and full occlusions. Our tracker better fits to tracking from aerial platforms as the scale change in successive frames are not dramatic.}
\label{fig:UAV123_DATASET}
\end{figure}

\begin{figure}
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=4.00cm]{./figures/Precision_OTB100.pdf}}
\bmvaHangBox{\includegraphics[width=4.0cm]{./figures/Success_OTB100.pdf}}\\
\end{tabular}
\caption{Evaluation and comparison of the proposed {\it E}nKCF tracker on the OTB100 dataset. OTB100 dataset consists of $100$ video sequences of different objects from recent literatures.}
\label{fig:OTB100_DATASET}
\end{figure}

\textbf{Performance on UAV123 Dataset.}  We compared the performance
of the proposed tracking algorithm with those of the state-of-the-art
high speed tracking algorithms in the \textit{Precision} and
\textit{Success\:Rate} metrics. Precision is computed by thresholding
the average euclidean distance between the centroid of the ground
truth and that of an tracking algorithm output.

{\it Burak: What do mean by the following sentence? We had graphs
  about precision, but I don't see any tables or anything else to rank
  the algorithms based on the precision at 20 pixels.}

{\it YoungWoo : Trackers are ranked in the legend in the graphs - the numbers next 
to each tracker is precision at 20 px and AUC for the success rate. It is how people rank
trackers in precision and success plots. I agree with you that we can have an additional table. Let me know what
you think about it now.}

In precision, we rank the trackers based on the precision numbers at
20 pixels.

The success rate metric counts how many outputs from a tracking
algorithm successfully overlap with those of the ground truth greater
than a given threshold. The overlap is specifically computed by the
Intersection-Over-Union (IoU) between a tracking output and that of
the ground truth. Given the number of the correct frames based an IoU
threshod, the success rate is the ratio of the correct frames to the
number of the total frames for testing.  In the success rate plots, trackers are
ranked based on AUC scores.

{\it Burak: After you remove some of the trackers, replace that number
  with ``some'' at the below as well as removing their names from the
  following paragraph.}

{\it YoungWoo :  I thought we were going to do that tomorrow. I have generated figures and 
I can easily remove any ones. SRDCF and MEEM are the top two as of now. I am working on removing them as of now. Please 
consider that we do not have SRDCF and MEEM while you are editing the results section.}

We compare our tracker to other high-speed ($\geq$300 fps)
state-of-the-art trackers including KCF\cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, STC\cite{zhang2014fast},
MOSSE\cite{bolme2010visual,henriques2015high}. Also, some relatively
lower-speed ($\geq$50) trackers are used to evaluate the robustness of
the proposed trackers. These trackers include SAMF\cite{li2014scale},
DSST\cite{danelljan2014accurate}, MEEM\cite{zhang2014meem}, Struck\cite{hare2012efficient}, and SRDCF\cite{danelljan2015learning}.
Fig.~\ref{fig:UAV123_DATASET} shows the results on the UAV123
dataset.

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications for embedded systems. This is primarily because most of
embedded systems already includes image acquisition pipeline and a
tremendous amount of progresses on research has been made for many
areas in computer vision. However, to successfully deploy a computer
vision algorithm on any existing embedded systems, a vision algorithm
needs to satisfy, at least, two criteria: minimal, manual intervention
after deployment and small footprint of computing resource consumption
and on executable code, with the assumption of reasonably good
performance. To this end, in this paper, we propose an ensemble of the
kernelized correlation filters (KCF), we call {\it E}nKCF, for a
single-target object tracking. In particular, we developed a committee
of KCFs to specifically address the scale-change and dynamic maneuver
of the target over frames. In addition, we devised a Bayes filter for
a smooth transition between individual KCFs' executions. Also, we
slightly modify the {\it E}nKCF to perform tracking in low frame rate
videos dominated by large ego-motion.  large ego-motion. Experimental
results showed that the performance of ours are 70.10\% for precision
on 20 pixels and 53.00\% for success rate for OTB100 data, and 54.50\%
and 40.2\% for UAV123 data. These results confirmed that our method
outperformed the existing ones over 5\% on precision on 20 pixels and
10-20\% on AUC on average. Our implementation ran at 340 fps for
OTB100 and at 416 fps for UAV123 data that is faster than DCF (292
fps) for OTB100 and KCF (292 fps), DCF (457 fps) for UAV123.
\end{abstract}

@@

The proposed algorithm, {\it E}nKCF, deploys three KCFs in turn: The
first filter, $R_{t}^{S}$, focuses on learning the target area and its
background, \textit{target}+\textit{small background} for addressing a
marginal translation by a target, the second filter, $R_{s}$, focuses
entirely on learning the target's scale, \textit{target-only}, and the
last filter, $R_{t}^{L}$, focuses on the target area and its
background twice bigger than that of the first filter, $R_{t}^{S}$,
\textit{target}+\textit{large background}. We set up {\it E}nKCF in
this way because we believe a correlation filter for learning a
target's translation should include its background to better
discriminate the target from its background and another correlation
filter is prepared to focus on the target itself to estimate the right
size or scale of the target. Fig.~\ref{fig:Filters} shows examples
of the region of interest (ROI) covered by each of three filters. We
believe that a filter for learning a target's translation should
include its background. In addition, making the ROI for the scale
filter, $R_{s}$, tighter reduces the size of the template for the
elementwise multiplication, resulting in a scale estimation in a
higher speed.
\begin{figure}[!h]
\centering
\includegraphics[width=0.4\textwidth]{figures/Filters_Details.pdf}
\caption{The three filters denoted as \textit{target+small background} translation filter,
  \textit{target-only} scale filter and \textit{target+large background} translation filters are
  shown. Also, the hanning window and desired Gaussian response for
  each filter is displayed.}
\label{fig:Filters}
\end{figure}

@@

In summary, the scale filter, $R_{s}$, is designed to directly handle
the scale change of a target and provides $R_{t}^{L}$ and $R_{t}^{S}$
with more focused ROIs about the target's translation. A translation
filter, $R_{t}^{L}$, is intended to look at a larger search area to
estimate the target's translation and recover from any potential
drifts. Another translation filter, $R_{t}^{S}$, on the other hand, is
designed to addresses the drawback of $R_{t}^{L}$ that it may learn
noisy shape features due to its large search area. Figure
\ref{Workflows} illustrates the workflow of the proposed
algorithm and alg.\ref{alg:MKCF} shows the pseudo-code of {\it
  E}nKCF. We do not have a seperate pseudeo-code for {\it E}nKCF2 as there are only two differences between 
  {\it E}nKCF and {\it E}nKCF2. First, the {\it E}nKCF2 runs $R_{t}^{L}$ every frame
to better tackle large ego-motion at low video frame rates. Second, we remove the particle filter in the {\it E}nKCF2 
tracker due to large ego-motion. In the following section, we will briefly mention the theory
behind the KCF.
\begin{algorithm}[h]
\small
	\caption{The {\it E}nKCF Tracking Algorithm.}\label{alg:MKCF}
	\begin{algorithmic}[1]
	\State \textbf{Input} : Initial bounding box $x_{0}$, frame counter $fc$, scale filter frequency $n = 5$,
	\State \textbf{Output} : 
				\If{$fc\:\%\:n=0$} \Comment{Condition 1}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
						Scale filter (\textit{target-only}) model $R_{s}$.
			     \EndIf
				\If{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=2$}\Comment{Condition 2}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t_1})$,
						Large Area Translation Filter model $R_{t}^{L}$.
				\EndIf
				\If{$fc\:\%\:n=3\:\:or\:\:fc\:\%\:n=4$}\Comment{Condition 3}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
						Small Area Translation Filter model $R_{t}^{S}$.
				\EndIf
	\Procedure{track}{$x_{t-1},y_{t-1},s_{t-1}$} 
				\State // Translation Estimation
				\State Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $x_{t} = (x_{t},y_{t},s_{t-1})$;
				\State // Translation Estimation
				\State Crop the ROI for the $R_{t}^{L}$, or $R_{t}^{S}$ given $x_{t}$
				and estimate translation ($x_{t}$,$y_{t}$) using $R_{t}^{L}$ (Condition 2) or $R_{t}^{S}$ (Condition 3),
				\State Skip translation estimation for $R_{s}$ (Condition 1);
				\State // Scale Estimation
			    \State Crop the ROI for the $R_{s}$ and estimate scale, $s_{t}$, using $R_{s}$ (Condition 1), 
				\State Scale pool for $R_{s}$ : $\lbrace1.05,1.0,1/1.05\rbrace$;
		        \State Skip it for $R_{t}^{L}$ and $R_{t}^{S}$ (Condition 1, and 2),
				\State // Update Translation
				\State Perform Importance Re-sampling (if necessary) for Particle Filter and compute the mean of posterior pdf $x_{t} = (x_{t},y_{t},s_{t})$;
			    \State // Model Update
			    \State Update $R_{s}$ (Condition 1);
			    \State Update $R_{t}^{L}$ (Condition 2);
			     \If{$PSR(y_{R_{t}^{S}}) \geq T_{R_{t}^{S}}$}
				\State Update $R_{t}^{S}$ (Condition 3);
			     \EndIf		
	\EndProcedure	
	\end{algorithmic}
\end{algorithm}
\begin{comment}
{\it Burak: The KCF section doesn't fit the section before and
  after. In addition, it's still too long.}

@@

\subsection{Kernelized Correlation Filter} \label{sec:kcf}
The Kernelized Correlation Filter tracker has recently been
increasingly popular due to its operation at hundreds of frames per
second with state-of-the-art tracking capabilities even in challenging
cases \cite{henriques2012exploiting,henriques2015high}. Its computational efficiency arises from its use of the
discrete fourier transform of the circulant matrix and frequency
domain. The KCF tracker minimizes the regularized ridge regression function shown below.
\begin{equation}
E(h) = \frac{1}{2}||y-\sum_{c=1}^{C}h_{c}*x_{c}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||h_{c}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where $y$ represents the desired continous response whereas $h$ and
$x_{c}$ represents the learned correlation filter and training
template for the given channel. The $c$ parameter included in
\cite{henriques2015high,galoogahi2013multi} makes it possible to
integrate multi-channel features such as HoG and colour into the ridge
regression function. The closed-form solution for the
eq.~\ref{eq:Closedform_RidgeReg} can be obtained by setting the
derivative of $E$ w.r.t $w$ to $0$. 
\begin{comment}The primal solution in the
frequency domain is formulated as
%\begin{equation}
%w = (X^{T}X+\lambda)^{-1}y
%\label{eq:SpatialSolution}
%\end{equation}
\begin{equation}
w = (X^{H}X+\lambda I)^{-1}X^{T}y
\label{eq:FourierSolution}
\end{equation}
where $X^{H}$ and $\lambda$represent the complex-conjugate of training
samples and regularization term. More documentation on the spatial and
fourier domain solutions can be found in \cite{henriques2015high}. The
MOSSE tracker uses one training sample centred at estimated position
of the target. This framework does not include enough background
information into the learned model,$w$. The application of the
circulant matrix theorem into the eq.~\ref{eq:Closedform_RidgeReg}
makes it possible to include many background patches at a similar
computational complexity. A circulant matrix includes the circularly
shifted patches of the positive training sample $x$ by a cylic shift
operator.

@@

In this form, the equation \ref{eq:FourierSolution} could prohibit us
from implementing a high speed object tracking as we need to perform
large number of element-wise division and multiplication
operations. However, we know from \cite{gray2006toeplitz} that all
circulant matrices are represented diagonally by the Fourier Transform
regardless of the base sample $x$.
%\begin{equation}
%X = Fdiag(\hat{x})F^{H},
%\label{eq:CirculantMatrixDFT}
%\end{equation}
%where $F$ denotes a constant Fourier Transform matrix and $x$ is the
%Discrete Fourier Transform of the base sample $x$. 
%To simplify the
%cost function formulation in eq.~\ref{eq:FourierSolution} we multiply
%$X$ in eq.~\ref{eq:CirculantMatrixDFT} with $X^{H}$ yielding
%\begin{equation}
%X^{H}X = Fdiag(\hat{x}^{*}\odot \hat{x})F^{H}.
%\label{eq:SimplificationX} 
%\end{equation}
\end{comment}
Then, the Circulant-matrix based solution vector in the Fourier domain $\hat{w}$ is formulated as
\begin{equation}
\hat{w} = \hat{x}^{*}*\hat{y}(\hat{x}^{*}*\hat{x}+\lambda)^{-1}.
\label{eq:DiagonalizedPrimalSolution}
\end{equation}
To further improve the robustness to geometric and photographic variations, one can exploit non-linear
regression function in the Correlation Filter framework \cite{henriques2015high}. 
%\begin{equation}
%\alpha = y(K+\lambda I)^{-1}
%\end{equation}
%where $K$ and $\alpha$ represent the kernel matrix and corresponding
%dual space solution. 
%\cite{henriques2015high} states that kernel
%matrices is circulant for datasets of circular cylic satisfying the
%following theorem.
%\begin{equation}
%k(x,x^{'}) = k(Mx,Mx^{'}),
%\label{eq:KernelCirculantTheorem}
%\end{equation}
%where $M$ represents the permutation matrix. Some kernels satisfying
%the eq.~\ref{eq:KernelCirculantTheorem} are \textit{Gaussian},
%\textit{Polynomial}, \textit{Intersection} and \textit{Hellinger}
%kernels. 
The diagonalized Fourier domain dual form solution can be
expressed as
\begin{equation}
\hat{\alpha} = \hat{y}(\hat{k}^{xx}+\lambda)^{-1}
\label{eq:FourierDualDomainSolution}
\end{equation}
where $\hat{k}^{xx}$ represents the first row of the Kernel matrix $K$
known as \textit{gram matrix} and it is expressed as
\begin{equation}
k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\hat{x}_{c}^{*}\odot \hat{x}_{c}^{'}))).
\label{eq:GaussianCorrelationSingleChannel}
\end{equation}
%\begin{equation}
%k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\hat{x}^{*}\odot \hat{x}^{'})))
%\label{eq:GaussianCorrelationSingleChannel}
%\end{equation}
The first correlation filter based trackers used grayscale feature ($C=1$) to
learn the solution vector $w$, however, multi-channel features
such as HoG and Color were later exploited to improve tracking
accuracy \cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. 
\begin{comment}The multi-channel feature integration into the Gaussian Kernelization
function in eq.~\ref{eq:GaussianCorrelationSingleChannel} is achieved
in a very straight-forward way by summing the correlation result over the channels.

Training shown in eq.~\ref{eq:FourierDualDomainSolution}
gives us $\hat{a}$ learned in time step $t$. We can accumulate
$\hat{a}$ over time to integrate more temporal information. This can
be expressed as
\begin{equation}
\hat{a}_{t} = (1-\beta)\hat{a}_{t-1} + \beta\hat{a}_{t}. 
\end{equation}
\end{comment}
Finally, detection step in multi-channel KCF framework is performed as
\begin{equation}
r(z) = F^{-1}(\hat{k}^{xz} \odot \hat{\alpha})
\end{equation}
where $r$ denotes the correlation response at all cylic shifts of the
first row of the kernel matrix.

@@

\textbf{Finding Optimal Hyperparameters} Each of three KCFs in {\it
  E}nKCF is designed for addressing a specific challenge of a single,
target tracking problem. Thus each of them should have different value
for the optimal parameters. For instance, the primary task of the
translation filter, $R_{t}^{L}$ is to estimate the translation of a
target from the previous frame whereas the scale filter, $R_{s}$ and
the estimated state of the particle filter are primarily used to
estimate the scale and translation. Because of this, we set the
learning rates ($\beta$) of individual filters, $R_{t}^{L}$,
$R_{t}^{S}$, and $R_{s}$ differently as $0.020$, $0.020$ and
$0.010$. For the kernel of the Gaussian neighboring function, we empirically
found the optimal values of $\alpha$ as $0.6$, $0.4$, and $0.4$ for
$R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$, and the learning rate as $0.12$
for $R_{t}^{L}$.

We tuned the number of particles in the particle filter to $1000$ after carrying out experiments, 
The re-sampling is only performed when the \textit{efficient number of samples} ($	\hat{N}_{eff} \approx (\sum_{p=1}^{P}w_{p}^{2})^{-1}
$) is lower than a pre-defined threshold. This way, we can continuously keep reasonable variance among particles.
\begin{equation}
	\label{eq:Neff_PF}
\end{equation}

@@

\textbf{Performance on UAV123 Dataset.}  We compared the performance
of the proposed tracking algorithm with those of the state-of-the-art
high speed tracking algorithms in the \textit{Precision} and
\textit{Success\:Rate} metrics. In precision, we rank the trackers based on the precision numbers at
20 pixels whereas in the success rate plots, trackers are
ranked based on area under curve (AUC) scores.

\begin{comment}
{\it Burak: What do mean by the following sentence? We had graphs
  about precision, but I don't see any tables or anything else to rank
  the algorithms based on the precision at 20 pixels.}

{\it YoungWoo : Trackers are ranked in the legend in the graphs - the numbers next 
to each tracker is precision at 20 px and AUC for the success rate. It is how people rank
trackers in precision and success plots. I agree with you that we can have an additional table. Let me know what
you think about it now.} 
\end{comment}

\begin{comment}
{\it Burak: After you remove some of the trackers, replace that number
  with ``some'' at the below as well as removing their names from the
  following paragraph.}

{\it YoungWoo :  I thought we were going to do that tomorrow. I have generated figures and 
I can easily remove any ones. SRDCF and MEEM are the top two as of now. I am working on removing them as of now. Please 
consider that we do not have SRDCF and MEEM while you are editing the results section.}
\end{comment}
We compare our tracker to other high-speed ($\geq$300 fps)
state-of-the-art trackers including KCF\cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, DCF\cite{henriques2015high}, and MOSSE\cite{bolme2010visual,henriques2015high}. Also, five relatively
lower-speed ($\geq$50) trackers are used to evaluate the robustness of
the proposed trackers. These trackers include SAMF\cite{li2014scale},
DSST\cite{danelljan2014accurate}, Struck\cite{hare2012efficient}, MUSTER \cite{hong2015multi}. TLD \cite{kalal2012tracking}, and
OAB \cite{zhang2012robust}. Fig.~\ref{fig:UAV123_OTB100_DATASET} shows the results on the UAV123
dataset.
